\section{Introduction}
\label{sec:intro}

A/B tests on tech platforms run in the thousands per day. The classical
fixed-horizon $t$-test assumes the sample size is chosen before looking
at the data. In practice analysts peek. They stop experiments that
look significant or extend those that look close, which inflates the
false-positive rate from $5\%$ to often $30\%$ or higher. The same
\emph{optional stopping} problem arises with higher stakes in clinical
trials. Interim analyses are essential there, but classical
group-sequential designs require the number and timing of looks to be
pre-specified. Anytime-valid confidence sequences~\cite{howard2021time,
waudbysmith2024estimating, whitehouse2025timeuniform} supply confidence
intervals valid at every stopping time simultaneously, removing this
constraint. The non-asymptotic flavour (Howard-Ramdas, betting,
Whitehouse vector) gives hard guarantees at every $t$. The
asymptotic flavour (time-uniform central limit theorem, CLT)
gives the looser large-sample
behaviour that governs deployment-scale runtime characteristics. The
benchmark covers both regimes, since deployed systems span both.

The theory is clean. The code that computes the confidence band is not.
A missing absolute value, an off-by-one on a log, a finite-precision
coarsening of the cumulant bound, or a dropped symmetry hypothesis can
each invalidate the nominal type-I guarantee while the software still
appears to run. A Lean~4 proof pinned against a fixed
Mathlib commit removes that class of error. Writing these proofs by
hand is labour-intensive: each theorem takes a trained
statistician-programmer hours to days. Closing them with language-model
drafters would reduce the manual proof effort required for production
deployment of anytime-valid methods. This paper benchmarks current drafters on a narrow, audited slice of that workload.

Existing Lean-proof benchmarks (MiniF2F~\cite{zheng2022minif2f},
ProofNet~\cite{azerbayev2023proofnet}, Verina~\cite{sunblazeverina})
measure the ability of a language-model drafter to close a proof
against a frozen statement library. Given a frontier Lean library with a specific conceptual
structure, which drafter capabilities are required to close theorems
about that structure, and can those capabilities be decomposed into
prompt-level interventions? To answer this we release \textsc{Formal-AVS},
a benchmark of $60$ Lean~4 theorems on anytime-valid confidence
sequences (CS)~\cite{howard2021time, waudbysmith2024estimating}.

\paragraph{Main finding.}
The T3 tier --- cross-family inequalities between rate functions ---
is a \emph{reasoning gap}, not a knowledge gap. Supplying the
log-domain substitution and the Mathlib lemma chain closes T3 to
$3$--$5/6$ per drafter; no drafter finds the chain autonomously
($0$--$1/6$ at baseline). This decomposition is the benchmark's
central result: the capability that separates Aristotle ($6/6$) from
the best generalist ($1/6$) is not access to the right lemmas but the
ability to discover the right rewrite without being told.
The targets cover sign and monotonicity of family-specific rate
functions, cross-function inequalities between the
HR-family~\cite{howard2021time}, betting
family~\cite{waudbysmith2024estimating}, Whitehouse
vector~\cite{whitehouse2025timeuniform}, and asymptotic CLT families,
and admissibility theorems for the four canonical stopping rules. A
\emph{target} in the rest of the paper means one of these $60$ Lean
theorem statements that a solver is asked to close. The companion
library is released under Apache-2.0 at the snapshot URL listed in the
supplementary archive (\texttt{REPRODUCE.md},
item~\textsc{lib-snapshot}). Quality assurance for the library
is described in~\S\ref{sec:methods-qa}. It includes
the axiom-clean baseline $\mathcal{A}_{\text{core}} \coloneqq
\{\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}\}$
enforced on every closed proof, manual review of all
$\sim$\,$50$ dependency lemmas, and Aristotle-surfaced refutations
of three statements.

The benchmark is paired with an Aristotle prover history archive.
Fourteen sessions of Harmonic Aristotle~\cite{aristotle2025} applied to
targets drawn from the same library are released alongside the
benchmark, with per-session verdicts
(closed / partial / refuted), closed Lean proofs, counterexample
witnesses, and \texttt{\#print axioms} audits. Prior Lean benchmarks
release target statements or solver traces, not both.

On a $48$-target evaluated slate, four closed-source generalists,
two specialised open-weights provers
(DSPv2-7B~\cite{dspv22025},
Goedel-Prover-V2-8B~\cite{goedelprover2025}), and Harmonic
Aristotle~\cite{aristotle2025} are evaluated across three
capability levels. Under single-shot $N{=}5$, generalist closure
saturates at $22/48$ (Gemini hint-list). T0 Mathlib-canon
targets return $0/28$ across four generalists. T3 cross-function
targets return $2/24$. Under agentic mode
(\texttt{cycle\_prove} $r{=}4$~\cite{opengauss2025}), Gemini
reaches $19/48$ and closes the first non-Aristotle T3 target.
The prompt-sensitivity gap narrows: Gemini's hint-list advantage
vanishes under agentic mode, suggesting the refinement loop
partially substitutes for prompt engineering
(\S\ref{sec:agentic}). Aristotle, under an unbounded compute
budget, closes $53/60$ axiom-clean and refutes three
false-as-stated targets (\S\ref{sec:aristotle-refute}).
We also report a 3-column T3 hint study
(\S\ref{sec:methods-hint-ablation}) and a prompt-sensitivity
matrix across all three capability levels
(Table~\ref{tab:prompt-sensitivity}).

\textsc{Formal-AVS} has four single-shape tiers (T0-T3) plus two
empirical failure categories. T4 contains four targets blocked by
missing Mathlib APIs. T5 contains one unresolved finite-precision
witness target. Tier shape: T0~($7$), T1~($34$), T2~($8$), T3~($6$),
T4~($4$), T5~($1$). Each theorem is annotated with a JSON record
containing statement, tier, required imports, per-drafter closure
rates at $N=5$, and a solver-status summary
(\S\ref{sec:methods-tiers}). Appendix~\ref{app:bench-format-fig}
(Listings~\ref{lst:bench-lean} and~\ref{lst:bench-json}) shows the
schema and a representative T3 target. T4 and T5 assignments depend on
observed solver behaviour and are flagged as such throughout the text.

This paper releases three artifacts.
(i) \texttt{formal-avs-lean}, an Apache-2.0 Lean~4 library authored as
a prerequisite for this benchmark ($\sim$\,$3$k lines, $8$ modules,
$\sim$\,$50$ axiom-clean dependency lemmas) that instantiates the four
canonical anytime-valid CS families and the rate functions required to
even state the cross-function targets.
(ii) A 60-theorem benchmark with T0-T3 single-shape tiers and T4-T5
empirical failure categories, plus per-drafter closure records and a
3-column T3 hint study.
(iii) A 14-session Aristotle history archive against the same library,
with closed/partial/refuted verdicts, closed Lean proofs, counterexample
witnesses, and axiom audits. The refutation track measures a capability
axis orthogonal to pass@$N$ closure: whether a solver can identify
false-as-stated theorems
(\S\ref{sec:aristotle-refute}).
