\section{Benchmark Construction}
\label{sec:methods}

We define a \emph{target} as a single Lean~4 theorem statement that a
solver is asked to close. \textsc{Formal-AVS} contains $60$ targets
(\S\ref{sec:methods-tiers}). Each is annotated with its tier, required
imports, family, and per-drafter closure record.
Appendix~\ref{app:bench-format-fig}
(Listings~\ref{lst:bench-lean} and~\ref{lst:bench-json}) shows one
target as Lean source and as a JSONL row. The field-level schema is
in Appendix~\ref{app:schema}.

\subsection{The companion library: \texttt{formal-avs-lean}}

We construct \texttt{formal-avs-lean}~\cite{formalavslean2026}, an
Apache-2.0 Lean~4 library released as a prerequisite artefact for
this benchmark. It instantiates the four canonical anytime-valid
confidence-sequence constructions, supplies per-family rate
functions $\eta_F$, and proves the dependency lemmas required to
even \emph{state} the cross-family inequalities used in T3. The
asymptotic CLT family is included for comparability with deployed
systems that mix non-asymptotic and asymptotic CS constructions.
The library is organised into eight modules (\texttt{Basic},
\texttt{HowardRamdas}, \texttt{WaudbySmithBetting},
\texttt{WhitehouseVector}, \texttt{AsymptoticCLT},
\texttt{Quantization}, \texttt{PhiTransform},
\texttt{MatchingConstants}). Target theorems are extracted from
each.

\textsc{Formal-AVS} contains $60$ targets by design:
target curation is bounded by the $\sim$\,$50$ axiom-clean dependency
lemmas a library author can hand-prove, which allows manual audit of
axiom use. Translation pipelines sourcing olympiad or textbook
content cannot reach the cross-family tier because Mathlib does not
instantiate the rate functions.

\paragraph{Why \texttt{formal-avs-lean} was necessary.}
Mathlib's \texttt{Probability.Martingale} supplies Doob decomposition
and Azuma's inequality but does not instantiate the four CS families,
the per-family rate functions, or Ville's inequality for the
betting-process construction. Without those, neither generalist
drafters nor Aristotle can attempt the T3 cross-function statements:
the goal type $\eta_{\mathrm{HR}}(b) \leq \eta_{\mathrm{vector}}(b)$
is not expressible. The library closes that gap in
$\sim$\,$3$k lines across $8$ modules and $\sim$\,$50$ dependency
lemmas, with the QA guarantees described in
\S\ref{sec:methods-qa}.

\subsection{Quality assurance and axiom audit}
\label{sec:methods-qa}

Because the benchmark grades drafters against the library, the library
itself must be trustworthy: a hidden \texttt{sorry} or a
silently-widened axiom set in any dependency lemma would invalidate
every closure built on top. Quality assurance has four components.
\textbf{(i)~Axiom-clean baseline.} Every reference proof, every closed
drafter attempt, and every closed Aristotle session terminates inside
the canonical Mathlib core $\mathcal{A}_{\text{core}} = \{\texttt{propext},
\texttt{Classical.choice}, \texttt{Quot.sound}\}$. The drafter-sweep
closure criterion (\S\ref{sec:methods-tiers}) rejects any candidate
whose \texttt{\#print axioms} dump extends beyond
$\mathcal{A}_{\text{core}}$, and per-target dumps union to exactly
$\mathcal{A}_{\text{core}}$ (Appendix~\ref{app:axiom-audit}). This
rules out the \texttt{axiom my\_lemma : \dots} shortcut.
\textbf{(ii)~Hand-authored dependency lemmas.} The $\sim$\,$50$
dependency lemmas (Ville's inequality, quantization-transport,
$\Phi$-substitution, sharp constants) were written by the library
authors before any solver run, and each was manually cross-checked
against the published constructions of
Howard et al.~\cite{howard2021time},
Waudby-Smith and Ramdas~\cite{waudbysmith2024estimating}, and
Whitehouse et al.~\cite{whitehouse2025timeuniform}.
\textbf{(iii)~Refutation discovery.} Three benchmark candidates
authored as legitimate targets were refuted by Aristotle on the first
attempt, and both original and corrected forms ship in the JSONL
(\S\ref{sec:aristotle-refute}).
\textbf{(iv)~Toolchain pinning} (\S\ref{app:reproducibility}): library,
JSONL, and verification driver are pinned to a fixed Lean toolchain
and Mathlib commit, and \texttt{bash reproduce.sh} re-runs the full
audit on cached outputs.

The dependency lemmas are sorry-free. Target theorems contain
\texttt{sorry} by design: these are the statements solvers attempt
to close, and the $53/60$ closed proofs are in the Aristotle history
and drafter output files.

\subsection{Tiers and failure categories}
\label{sec:methods-tiers}

Each target carries two kinds of label. The four \emph{tiers} T0-T3
are assigned by theorem shape before any drafter run. The two
\emph{empirical failure categories} T4 and T5 are assigned
after evaluation, because their definitions reference observed
solver behaviour. We separate the two kinds of label so that the
tier signal is independent of solver outcome.

\paragraph{Pre-evaluation tiers (T0-T3).}
\textbf{T0} (Mathlib canon, $7$ theorems): statement and proof
expressible entirely within Mathlib (sanity-check floor).
\textbf{T1} (single-function friendly, $34$): sign /
monotonicity / positivity of a single $\eta_F$ closeable by
\texttt{positivity}, \texttt{nlinarith}, or a short
\texttt{simp}-chain.
\textbf{T2} (single-function challenging, $8$): single-function
targets whose closure requires a substitution or a Mathlib
lemma not named in the goal.
\textbf{T3} (cross-function inequality, $6$): inequalities
or sharp-constant identities between two rate functions (e.g.\
$\eta_{\mathrm{vector}} = \sqrt{2}\,\eta_{\mathrm{HR}}$),
admitting a log-domain $\Phi$-substitution. T0-T3 assignment
depends only on theorem signature and is fixed before any
drafter sweep.

\paragraph{Empirical failure categories (T4, T5).}
\textbf{T4} (library-gap, $4$ theorems): targets where no
evaluated solver returned a closure and the missing piece is a
Mathlib API not yet upstream (sub-Gaussian MGF bound for
martingale sums, Ville's inequality for supermartingales,
vector concentration, time-uniform CLT). A Mathlib pull request
adding the required API would move these targets out of T4.
\textbf{T5} (unresolved, $1$ theorem): the sole T5 target,
\texttt{equivalence\_\allowbreak break\_at\_\allowbreak finite\_precision}, has zero
close-rate across every evaluated solver. It is a
witness-construction problem on the continuous-equivalence
break between Howard-Ramdas and Ville thresholds at finite
precision; no missing Mathlib API explains the failure.
T4 and T5 are empirical categories from this evaluation, not predictions for future solvers.

\subsection{Drafter sweep protocol}

Each drafter is evaluated at $N=5$ attempts per target under a
mixed-temperature schedule: one greedy attempt (temperature
$T=0$) followed by four independent samples at $T=0.7$. The
attempt budget is $8$k tokens per sample. We define pass@$N$ at
the target level. A target is \emph{closed} for a drafter if at
least one of the $N$ attempts produces a Lean~4 proof that
(a)~type-checks on the specified toolchain, (b)~closes the goal
with no residual \texttt{sorry}, and (c)~does not widen the
axiom set beyond $\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$.
Pass@$N$ is defined at the target level: a target is closed if any
of the $N$ attempts succeeds. We do not aggregate over individual
attempts as if they were independent samples.

\paragraph{Target-selection protocol.}
We extracted target theorems from the eight
\texttt{formal-avs-lean} modules. The selection criteria,
applied in order, were the following.
(i)~The theorem is provable in Lean~$4$ against Mathlib at the
pinned commit, modulo the dependency lemmas already proved
inside \texttt{formal-avs-lean}.
(ii)~The statement does not import a non-Apache-2.0 third-party
library.
(iii)~The statement is at most $400$ characters and does not
require a custom tactic block to state.
We did not pre-screen for drafter difficulty. Of the
$\sim$\,$120$ candidate theorems in the library, $60$ met the
criteria and form the released benchmark. The remaining
candidates were excluded for reasons recorded per-target in the
supplementary \texttt{selection\_log.csv}.

\paragraph{Evaluated slate.}
The headline drafter sweeps were run on a $48$-target subset.
The $48$-slate is the canonical evaluation set in this
submission. The full $60$-target table adds $4$ T4 entries,
$1$ T5 entry, and $7$ T1 entries that we report separately
(see Table~\ref{tab:headline}, footnote on imputed cells).
T4 and T5 entries are zero by construction in the
$60$-target table because they were assigned to those
categories on the basis of zero closures across evaluated
solvers (\S\ref{sec:methods-tiers}). We report headline rates
on the $48$-slate and a status table on $60$ targets, rather
than fold the two together.

\paragraph{Drafter set.}
Four closed-source drafters are scored in the headline sweep.
Claude Sonnet~4.6, Kimi~K2.5, and Gemini~3 Pro under a shared
hint-list prompt. Mistral Large~3 under a neutral prompt
(\S\ref{sec:spec-inversion} reports the prompt-sensitivity
result). Mistral collapses to $0/240$ on the same hint-list
prompt because of greedy hint-list compliance, so the headline
row uses the prompt that produces a non-degenerate row.
Cross-drafter aggregates over Mistral and the other three
should be read with this prompt asymmetry in mind. A
supplementary closed-source row, Claude Opus~$4.6$, is reported
on the same $48$-slate at $N=5$ under the hint-list prompt.
Two specialised open-weights drafters complete the headline sweep:
DeepSeek-Prover-V2-7B~\cite{dspv22025}
(\href{https://huggingface.co/deepseek-ai/DeepSeek-Prover-V2-7B}{huggingface.co/deepseek-ai/DeepSeek-Prover-V2-7B})
and Goedel-Prover-V2-8B~\cite{goedelprover2025}
(\href{https://huggingface.co/Goedel-LM/Goedel-Prover-V2-8B}{huggingface.co/Goedel-LM/Goedel-Prover-V2-8B}).
Both are scored on the $48$-slate at $N=5$ under the same neutral
specialised-prover prompt template. Community quantization choices
and reproduction details are in Appendix~\ref{app:prompts}. DSPv2
attempts are released as cached candidates in the supplementary
archive. The Goedel-V2 row is reproducible end-to-end from the
released weights and evaluation driver.

\subsection{Hint ablation protocol}
\label{sec:methods-hint-ablation}

Three prompt columns per T3 target are evaluated, with names chosen
so the content is recoverable from the label.
\textbf{\textsc{Base}}: goal statement only (no-hint baseline).
\textbf{\textsc{Sub}}: \textsc{Base} plus a one-line
$\Phi$-substitution hint
$x \mapsto \exp(\lambda^{\star} x - (\lambda^{\star})^{2}\sigma^{2}/2)$,
with family-specific $\lambda^{\star}$ (isolates lemma search given
the substitution). \textbf{\textsc{Sub+Chain}}: \textsc{Sub} plus an
explicit Mathlib lemma chain (\texttt{Real.exp\_le\_one\_iff},
\texttt{Real.log\_nonneg}, \texttt{Real.sqrt\_le\_sqrt}, \dots) with
usage-direction annotations (isolates lemma application given both).
A boxed-table form is Table~\ref{tab:hint-legend}
(Appendix~\ref{app:hint-legend-table}). The five-stage evaluation
pipeline is expanded as Table~\ref{tab:eval-protocol}
in Appendix~\ref{app:eval-protocol-fig}.

The \textsc{Sub+Chain} lemma list was reverse-engineered from an
Aristotle T3 closure (\S\ref{sec:methods-tiers}, footnote on
hint-chain provenance). An alternative library-reference chain
(\S\ref{app:alternative-hint-chain}) is released as a sensitivity
check, overlapping on $5/7$ lemmas. We read \textsc{Sub+Chain} as a
proof-plan-condition upper bound on drafter T3 closure given the
lemma chain, not as an independent tactic-vocabulary measurement.

\subsection{Aristotle history collection}

Fourteen Harmonic Aristotle~\cite{aristotle2025} sessions were
collected between 2026-03 and 2026-04 against the same
\texttt{formal-avs-lean} library. Each session submits $1$ to
$5$ targets. We record per-target verdict (\texttt{closed},
\texttt{partial}, or \texttt{refuted}), the closed Lean proof
when applicable, the counterexample when applicable, the
axiom-set dump of the closed Lean kernel, and the fingerprint
hash of the submitted Lean tarball. All 14 sessions are
released as \texttt{aristotle\_history.jsonl} alongside the
benchmark. Reproducing a session against the released library
requires a Harmonic API key (we accessed Aristotle through the
public dashboard at \url{aristotle.harmonic.fun}).

\paragraph{Refutation handling.}
Three benchmark targets were authored as legitimate library
statements but Aristotle returned counterexamples on first
attempt, identifying that the as-stated forms were
mathematically false (\S\ref{sec:aristotle-refute}). We retain
all three in the benchmark JSONL. The released schema includes
both the corrected theorem (used in headline drafter sweeps and
the Aristotle 53/60 closure count) and the original refuted
form (used to support the statement-correctness classification
axis). Refutations were not seeded by the authors. They are a
discovered property of the library that the benchmark surfaces
and preserves.

\paragraph{Aristotle compute budget.}
Each Aristotle session is a single API call submitted via
\texttt{aristotle submit} against the released library. We did
not impose a per-session token or rollout cap. Sessions return
on average within $30$ to $50$ minutes of wall time.
Drafters are scored at $N=5$ attempts of $8$k tokens each.
The Aristotle vs.\ drafter comparison is therefore between a
proof-search system with unbounded internal compute and a
generalist drafter at a fixed token budget. The $53/60$
vs.\ $2/24$ T3 gap conflates training data, training scale,
search compute, and prompt-conditioned tactic vocabulary, and
is reported as such.

\paragraph{Reproducibility.}
The supplementary archive includes the \texttt{formal-avs-lean}
library at the cited Lean toolchain and Mathlib pin (toolchain
reference and Mathlib commit are listed in the supplementary
\texttt{REPRODUCE.md}), the benchmark JSONL with both corrected
and original (refuted) statement forms, the prompt files, the
drafter sweep driver, the Wilson-CI computation script, and the
Lean kernel verification script that recomputes the
$\{\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}\}$
axiom audit. A single command (\texttt{bash reproduce.sh}) runs
the verification pipeline on cached drafter outputs to
regenerate every numeric cell in the headline tables. Drafter
output files for all evaluated cells are released in the
archive.
