\section{Background and related work}
\label{sec:related}

\paragraph{Anytime-valid confidence sequences.}
A confidence sequence $(C_t)_{t \geq 1}$ at level $1 - \alpha$ for a
parameter $\mu$ is a sequence of random intervals satisfying
$\Prob(\forall t \geq 1: \mu \in C_t) \geq 1 - \alpha$. The four
canonical constructions for bounded-mean or sub-Gaussian settings
each specify an exponential supermartingale
$M_t = \exp(\lambda S_t - \psi_F(\lambda) t)$ with a family-specific
cumulant-bound function $\psi_F$. Ville's inequality applied to
$M_t$ produces a $1-\alpha$ CS with half-width
$\eta_F(\alpha, t) = (\psi_F^{-1} \circ \text{lin})(\alpha, t)$. The
benchmark targets theorems about these four
$\eta_F$~\cite{howard2021time, waudbysmith2024estimating,
whitehouse2025timeuniform}, their monotonicity, sign, and
cross-family inequalities.

\paragraph{Lean proof benchmarks.}
MiniF2F~\cite{zheng2022minif2f} covers competition arithmetic.
ProofNet~\cite{azerbayev2023proofnet} covers undergraduate
analysis, algebra, and topology.
Verina~\cite{sunblazeverina} targets verifiable code generation
with $189$ Lean tasks. \textsc{FormalMATH}~\cite{formalmath2025}
contains $5{,}560$ Lean~4 theorems from olympiad to
undergraduate level. LeanDojo~\cite{yang2023leandojo} extracts
training and evaluation theorems from Mathlib.
REAL-Prover~\cite{realprover2024} and
LeanAgent~\cite{leanagent2024} mine Mathlib-adjacent
undergraduate content. \textsc{Formal-AVS} differs in target
domain: a Lean benchmark focused on a research subfield not
currently represented in Mathlib, with axiom-audited dependency
proofs and a cross-family inequality tier.

\paragraph{Harmonic Aristotle and prover-history archives.}
The companion archive uses Harmonic's Aristotle
prover~\cite{aristotle2025}, a closed-source proprietary Lean~4
proof-search engine with axiom-audit and counterexample-extraction
hooks, and distinguishes genuine closures from drafter
hallucinations via machine-checked Lean kernel certificates.
Aristotle is not an open-weights model. We accessed it through
the public API at \url{aristotle.harmonic.fun} at no cost during
benchmark construction. Closure verdicts and counterexample
witnesses are reproducible from the released session IDs, but
re-running an Aristotle session against the released library
requires a Harmonic API key. The closest prior
artefact is LeanDojo's tactic-trace dataset. Our companion artefact
differs in three ways: (i) Aristotle sessions rather than Mathlib
commits, (ii) refutation traces with counterexample witnesses, and
(iii) per-session axiom-audits (Lean \texttt{\#print axioms}
output). The third property is important for evaluating prover
trustworthiness: drafter-produced Lean proofs may close the goal but
widen the axiom set~\cite{yang2023leandojo}.

\paragraph{Hint-ablation methodology.}
Prompt-hint ablation for Lean drafters has been studied in the
context of tactic-premise selection~\cite{polu2020gpt, han2022proof,
jiang2023draftsketchandprove} and proof-sketch scaffolding. Most
prior studies treat hints as a single ``context'' axis and measure
gross closure-rate gain. \textsc{Formal-AVS} decomposes the hint
into two orthogonal components, a log-domain substitution hint
(\emph{lateral re-encoding}) and a Mathlib-lemma-chain hint
(\emph{tactic vocabulary}), and measures their effects independently
across four drafter classes plus one specialised $7$B prover. The
3-column ablation (\S\ref{sec:results}) shows neither component alone
is sufficient. Closure rates increase only when both are supplied to
mid-tier generalists.

\paragraph{Agent-style evaluation of code and proof drafters.}
Single-shot benchmarks understate drafter capability: the same
models close many more issues when granted file navigation, multi-step
tool calls, and execution feedback, as shown by
SWE-bench~\cite{jimenez2024swebench, chowdhury2024swebenchverified}.
Agentic frameworks for theorem proving and code/database
editing are emerging in
parallel~\cite{liu2024agentbench, wang2024mathcoder}. \textsc{Formal-AVS} supports both completion- and
agent-style evaluation. A target's JSON record exposes the tier
shape, required imports, and the $\mathcal{A}_{\text{core}}$ axiom
audit, which are the inputs an agentic evaluation loop consumes when delegating
to a Lean kernel. The headline sweep is the completion-style baseline
against which the agentic-mode gain reported in
Table~\ref{tab:prompt-sensitivity} is measured.

\paragraph{Anytime-valid CS formalisations.}
No prior public Lean~4 library formalises the HR-family, betting
family, Whitehouse vector, or asymptotic CLT confidence-sequence
families. The mathlib \texttt{Probability.Martingale}
module~\cite{mathlib4-probability} supplies Doob decomposition and
Azuma's inequality but does not instantiate the four CS families or
their sharp-constant comparison inequalities. The
\texttt{formal-avs-lean} library (released with this benchmark)
instantiates all four families, supplies Ville's inequality and the
quantization-transport lemma, and exposes 29 theorems that require
library-specific definitions.
