\section{Results}
\label{sec:results}

\subsection{Per-tier results on the evaluated 48-slate}

Table~\ref{tab:headline} reports per-drafter closure rates at
$N=5$ on the evaluated $48$-slate (T0-T3 shapes), plus a
$60$-target status table. T4 and T5 entries are zero in the
$60$-target table by construction
(\S\ref{sec:methods-tiers}). Aristotle's closure rate is in
\S\ref{sec:capability-ladder}. Most drafter closures fall on
T1; the other five tiers show low closure.

\textbf{T0} ($0/28$ across 4 generalists): generalists fail on
Mathlib-canon lemmas despite these appearing in training corpora.
The failure mode is a tactic-prior mismatch: drafters attempt
multi-step rewrites where a single \texttt{simp} or
\texttt{exact?} suffices, because the \texttt{formal-avs-lean}
namespace context shifts the tactic distribution away from the
Mathlib patterns the models memorised
(\S\ref{app:t0-stripped-prompt}).
\textbf{T2} ($0/8$): requires a substitution or unnamed
Mathlib lemma.
\textbf{T3} ($2/24$): drafter close-rate $0$--$1/6$. Aristotle
closes $6/6$. The gap is a system difference, not per-token
(\S\ref{sec:agentic}).
\textbf{T4} ($0/4$): blocked by missing Mathlib APIs (Ville,
sub-Gaussian MGF, vector concentration, time-uniform CLT).
\textbf{T5} ($0/1$): Aristotle refuted the as-stated form
(\S\ref{sec:aristotle-refute}). Corrected form unresolved.

\begin{table}[t]
\centering
\small
\caption{Per-drafter closure rates on the $48$-slate at $N{=}5$
(one greedy $+$ four $T{=}0.7$ samples). Overall column sums the
$60$-target status table ($12$ extras $0$-imputed; T4/T5 zero by
construction). Wilson CIs in Appendix~\ref{tab:wilson-ci}.
See Appendix~\ref{app:robustness-n10} for $N{=}10$ results.}
\label{tab:headline}
\resizebox{\textwidth}{!}{%
\begin{tabular}{lccccccccc}
\toprule
Drafter & T0 & T1 & T2 & T3 & T4 & T5 & overall pass@1$^{\ddagger}$ & pass@5 & pass@10$^{\dagger}$ \\
\midrule
Claude Sonnet~4.6  & 0/7 & 18/34 & 0/8 & 0/6 & 0/4 & 0/1 & 11/60 & 18/60 & 18/60 \\
Kimi~K2.5          & 0/7 & 17/34 & 0/8 & 1/6 & 0/4 & 0/1 & 13/60 & 18/60 & 18/60 \\
Gemini~3 Pro       & 0/7 & 22/34 & 0/8 & 0/6 & 0/4 & 0/1 & 9/60 & 22/60 & 23/60 \\
Mistral Large~3$^{\ast}$ & 0/7 & 1/34 & 0/8 & 1/6 & 0/4 & 0/1 & 0/60 & 2/60 & 2/60 \\
Claude Opus~4.6$^{\ddagger\ddagger}$ & 0/7 & 13/34 & 0/8 & 0/6 & 0/4 & 0/1 & 13/60 & 13/60 & 14/60 \\
DSPv2-$7$B GPTQ-int8$^{\S}$ & 3/7 & 8/34 & 0/8 & 1/6 & 0/4 & 0/1 & 10/60 & 12/60 & 13/60 \\
Goedel-Prover V2-Q6\_K$^{\P}$ & 2/7 & 3/34 & 0/8 & 0/6 & 0/4 & 0/1 & 4/60 & 5/60 & 6/60 \\
\bottomrule
\end{tabular}}
\vspace{0.3em}

{\footnotesize $^{\ast}$Mistral on neutral prompt ($0/240$ on hint-list).
$^{\ddagger\ddagger}$Opus on hint-list only.
$^{\S}$DSPv2 on neutral prompt.
$^{\P}$Goedel-V2 GGUF Q6\_K on neutral prompt.
$^{\dagger}$pass@10 adds 3 new closures.}

\end{table}

\phantomsection
\paragraph{Capability ladder: single-shot $\to$ agentic $\to$ Aristotle.}
\label{sec:capability-ladder}
Three capability levels are evaluated on the same slate.

\paragraph{Hint ablation (T3).} A 3-column T3 hint study
(\textsc{Base}, \textsc{Sub}, \textsc{Sub+Chain}) is reported in
Appendix~\ref{app:hint-ablation-table}. Generalist closure on
T3 rises from $0$--$1/6$ at \textsc{Base} to $3$--$5/6$ at
\textsc{Sub+Chain}. The \textsc{Sub+Chain} chain was
reverse-engineered from an Aristotle closure, so we read it
as an upper bound (sensitivity check in
Appendix~\ref{app:alternative-hint-chain}).

\subsection{Prompt-sensitivity is drafter-specific and bidirectional}
\label{sec:spec-inversion}

Table~\ref{tab:prompt-sensitivity} reports per-drafter closure
rate under both the shared hint-list prompt (which enumerates
nine allowed Mathlib tactics as suggestions and asks for minimal
proofs) and a neutral prompt that omits the enumeration
(``Close this theorem with a clean Lean~4 proof. Use any Mathlib
tactic.''). Both evaluated on the same $48$-target drafter-testable
slate at $N=5$ (one greedy $T=0$ + four $T=0.7$).

\begin{table}[t]
\centering
\small
\caption{Capability ladder: prompt-sensitivity across single-shot,
agentic, and Aristotle on the $48$-slate (pass@$5$). Single-shot
uses $N{=}5$ ($1$ greedy $+$ $4$ stochastic). Agentic uses
\texttt{cycle\_prove} $r{=}4$
(draft $\to$ \texttt{lake build} $\to$ refine,
default from OpenGauss~\cite{opengauss2025}).
Hint-list enumerates nine Mathlib tactics.
Neutral omits the enumeration. Aristotle~\cite{aristotle2025}
operates under an unbounded compute budget (no prompt
distinction). The hint-list advantage shrinks under agentic mode:
Sonnet's $6\times$ single-shot lift ($3 \to 18$) reduces to
$15\%$ ($13 \to 15$). Gemini's advantage vanishes ($19 = 19$):
per-target lake errors substitute for the static tactic
enumeration.}
\label{tab:prompt-sensitivity}
\begin{tabular}{lcc}
\toprule
Drafter & Hint-list & Neutral \\
\midrule
\multicolumn{3}{l}{\emph{Single-shot ($N{=}5$)}} \\
\quad Gemini~3 Pro            & 22/48 & 13/48 \\
\quad Claude Sonnet~4.6       & 18/48 &  3/48 \\
\quad Kimi~K2.5               & 18/48 & 13/48 \\
\quad DSPv2-$7$B              & 12/48 &  9/48 \\
\quad Goedel-V2-Q6\_K         &  5/48 &  3/48 \\
\quad Mistral Large~3         &  0/48 &  2/48 \\
\midrule
\multicolumn{3}{l}{\emph{Agentic (\texttt{cycle\_prove} $r{=}4$)}} \\
\quad Gemini~3 Pro            & 19/48 & 19/48 \\
\quad Claude Sonnet~4.6       & 15/48 & 13/48 \\
\quad Goedel-V2-Q6\_K         & 10/48 & 13/48 \\
\midrule
Aristotle (unbounded)         & \multicolumn{2}{c}{53/60} \\
\bottomrule
\end{tabular}

\end{table}

The hint-list helps three of four generalists and reduces
Mistral ($2/48 \to 0/48$). Sonnet's sensitivity is largest
($6\times$). Extended per-drafter analysis in
Appendix~\ref{app:prompt-sensitivity-detail}.\footnote{Four
extended analyses are in Appendix~\ref{app:extended}: Aristotle
history, companion closures, cross-drafter tactic diversity, and
the no-closure tail.}


\subsection{Capability ladder: single-shot, agentic, and Aristotle}
\label{sec:agentic}

Closure rate increases monotonically across three capability levels
on the same slate: \emph{single-shot} (best-of-$N$, no error
feedback), \emph{agentic} (draft $\to$ \texttt{lake build} $\to$
feed errors back $\to$ refine, $r{=}4$ rounds), and
\emph{Aristotle} (unbounded internal refinement). Harmonic
Aristotle~\cite{aristotle2025} closes $53/60$ axiom-clean ($7/7$
T0, $33/34$ T1, $7/8$ T2, $6/6$ T3) plus $3$ refuted
(\S\ref{sec:aristotle-refute}). Companion-archive closures are
in \S\ref{app:aristotle-companion}. Under \texttt{cycle\_prove}
$r{=}4$:

\begin{itemize}[leftmargin=1.3em, itemsep=0.15em]
\item \textbf{Gemini~3~Pro.} Single-shot neutral $13/48$ $\to$
  agentic $19/48$ ($46\%$ lift). Gemini agentic closes
  \texttt{ranking\_four\_way} (T3) on round~$2$: the first
  non-Aristotle closure on a cross-function target.
\item \textbf{Sonnet~4.6.} Neutral $3/48$ $\to$ agentic $15/48$
  ($5\times$ lift from the refinement loop alone).
\item \textbf{Goedel-V2-Q6\_K.} Single-shot $5/48$ $\to$ agentic
  $13/48$ ($2.6\times$ lift). Goedel-V2 was trained with
  verifier-guided self-correction~\cite{goedelprover2025}: the
  model uses Lean compiler feedback to iteratively revise its
  proofs. Under \texttt{cycle\_prove} this training activates and
  Goedel surpasses DSPv2's single-shot $9/48$, becoming the
  strongest local prover on our slate at \$0 marginal cost.
\end{itemize}

The prompt-sensitivity gap narrows under cycle\_prove. Sonnet's
single-shot $6\times$ hint-list advantage ($3/48 \to 18/48$) reduces
to $15\%$ under agentic ($13 \to 15$). Gemini's advantage disappears
($19 = 19$). Per-target lake errors provide stronger signal than a
static tactic list, partially substituting for prompt engineering.

Across both drafters, $14$ targets close under both, $5$ are
Gemini-only (including $2$ T3 cross-function targets), $1$ is
Sonnet-only. Most closures land on rounds $1$--$2$ ($28/34$).
Rounds $3$--$4$ contribute $6/34$: the refinement loop's value is
primarily one error-correction cycle, not deep multi-round search.
Generalist single-shot saturates below $22/48$, agentic $r{=}4$
reaches $19/48$, and Aristotle's open-ended budget closes $53/60$.
The hint ablation (Table~\ref{tab:ablation}) shows the
tactic vocabulary is latent in the generalist drafters; the gap
is attributable to search depth, not missing knowledge.

\subsection{Refutation findings}
\label{sec:aristotle-refute}

Beyond closure, Aristotle refuted three benchmark targets whose
as-stated form is mathematically false, returning machine-checkable
counterexamples on each: \texttt{equivalence\_\allowbreak break\_at\_\allowbreak finite\_precision}
(T5, missing symmetry hypothesis), \texttt{slack\_antitone\_in\_scale}
(T2, missing bits-match hypothesis, counterexample
\texttt{bp$_1$=(1,1)}, \texttt{bp$_2$=(2,1)}), and
\texttt{div\_le\_div\_of\_nonneg\_left} (T1, typo in direction:
\texttt{a=1,b=2,c=3} gives \texttt{1/2 > 1/3}). Each corrected form
was subsequently proved.

\paragraph{Provenance of the three refutations.}
These statements were authored as legitimate library targets prior
to any solver run. Aristotle subsequently flagged each as-stated
form as false on its first attempt. The refutations were not
seeded into the benchmark by the authors. The benchmark JSONL
contains the corrected forms in the headline target column and the
original false-as-stated forms in a parallel \texttt{refuted\_form}
field.

The mix of correct, borderline, and false-as-stated targets
therefore supports a second evaluation axis: \emph{statement-correctness
classification} via refutation. Pass@$N$ solvers that do not
attempt counterexample construction miss this axis entirely.
